Incorporating dive behaviour into models of marine animal movement

### 2018-10-04 manuscript/manuscript_template.Rmd
Add keywords to abstract

abstract: |
 The Abstract must not exceed 350 words and should list the main results and conclusions, using simple, factual, numbered statements.  
 1. Models of animal movement often only consider horizontal movement over 2 dimensions. Incorporating vertical movement in these models offers the potential to improve our understanding of the drivers of animal movement.  
 2. Here we describe a state-space model that incorporates a random walk on both horizontal and vertical movements, and estimates the covariance between them. The model is flexible to allow both parameters to be conditioned on covariates, offering insights into the drivers of animal movement.  
 3. outline the main results  
 4. identify the conclusions and the wider implications.

keywords: | 
 A list in alphabetical order not exceeding eight words or short phrases. The most important key-words should appear in the title and the abstract as well as the key-word list.

date: "`r format(Sys.time(), '%d %B %Y')`"
output:
  pdf_document:
    fig_caption: yes
    keep_tex: yes
    number_sections: yes
  html_document:
    fig_caption: yes
    force_captions: yes
    highlight: pygments
    number_sections: yes
    theme: cerulean
csl: mee.csl
bibliography: references.bib
header-includes:
   - \usepackage{lineno}
   - \linenumbers
   - \usepackage{setspace}
   - \doublespacing
fontsize: 12pt
---

>>>>

date: "`r format(Sys.time(), '%d %B %Y')`"

abstract: |
 The Abstract must not exceed 350 words and should list the main results and conclusions, using simple, factual, numbered statements.  
 1. Models of animal movement often only consider horizontal movement over 2 dimensions. Incorporating vertical movement in these models offers the potential to improve our understanding of the drivers of animal movement.  
 2. Here we describe a state-space model that incorporates a random walk on both horizontal and vertical movements, and estimates the covariance between them. The model is flexible to allow both parameters to be conditioned on covariates, offering insights into the drivers of animal movement.  
 3. outline the main results  
 4. identify the conclusions and the wider implications.  
 **keywords:** A list in alphabetical order; not exceeding eight words or short phrases; The most important key-words should appear in the title; and the abstract; as well as the key-word list.

output:
  pdf_document:
    fig_caption: yes
    keep_tex: yes
    number_sections: yes
  html_document:
    fig_caption: yes
    force_captions: yes
    highlight: pygments
    number_sections: yes
    theme: cerulean
csl: mee.csl
bibliography: references.bib
header-includes:
   - \usepackage{lineno}
   - \linenumbers
   - \usepackage{setspace}
   - \doublespacing
fontsize: 12pt
---

### 2018-10-04 manuscript/manuscript_template.tex
Add keywords to abstract

\documentclass[]{article}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\usepackage[margin=1in]{geometry}
\usepackage{hyperref}
\hypersetup{unicode=true,
            pdftitle={Incorporating dive behaviour into models of marine animal movement},
            pdfkeywords={A list in alphabetical order not exceeding eight words or short phrases.
The most important key-words should appear in the title and the abstract
as well as the key-word list.},
            pdfborder={0 0 0},
            breaklinks=true}
\urlstyle{same}  % don't use monospace font for urls
\usepackage{longtable,booktabs}
\usepackage{graphicx,grffile}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
\IfFileExists{parskip.sty}{%
\usepackage{parskip}
}{% else
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{5}
% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

@@

  \title{Incorporating dive behaviour into models of marine animal movement}
    \pretitle{\vspace{\droptitle}\centering\huge}
  \posttitle{\par}
    \author{W. J. Grecian\(^1\) \footnote{Corresponding author:
  \href{mailto:james.grecian@gmail.com}{\nolinkurl{james.grecian@gmail.com}}}
, I. D. Jonsen\(^2\)\\
\(^1\)Sea Mammal Research Unit, Scottish Oceans Institute, University of
St Andrews\\
\(^2\)Dept. of Biological Sciences, Macquarie University, Sydney,
Australia}
    \preauthor{\centering\large\emph}
  \postauthor{\par}
      \predate{\centering\large\emph}
  \postdate{\par}
    \date{03 October 2018}

\usepackage{lineno}
\linenumbers

\begin{document}
\maketitle
\begin{abstract}
The Abstract must not exceed 350 words and should list the main results
and conclusions, using simple, factual, numbered statements.\\
1. Models of animal movement often only consider horizontal movement
over 2 dimensions. Incorporating vertical movement in these models
offers the potential to improve our understanding of the drivers of
animal movement.\\
2. Here we describe a state-space model that incorporates a random walk
on both horizontal and vertical movements, and estimates the covariance
between them. The model is flexible to allow both parameters to be
conditioned on covariates, offering insights into the drivers of animal
movement.\\
3. outline the main results\\
4. identify the conclusions and the wider implications.
\end{abstract}

@@

\begin{longtable}[]{@{}lrrrr@{}}
\caption{This is a GLM summary table.}\tabularnewline
\toprule
& Estimate & Std. Error & t value &
Pr(\textgreater{}\textbar{}t\textbar{})\tabularnewline
\midrule
\endfirsthead
\toprule
& Estimate & Std. Error & t value &
Pr(\textgreater{}\textbar{}t\textbar{})\tabularnewline
\midrule
\endhead
(Intercept) & 0.01 & 0.10 & 0.07 & 0.94\tabularnewline
x & 1.83 & 0.11 & 16.95 & 0.00\tabularnewline
\bottomrule
\end{longtable}

@@

The relationship was first described by @Halpern\_2006. However, there
are also opinions that the relationship is spurious {[}@Keil\_2012{]}.
We used R for our calculations {[}@R\_Core\_Team\_2016{]}, and we used
package \texttt{knitcitations} {[}@Boettiger\_2017{]} to make the
bibliography.

@@

\section{REFERENCES}\label{references}

>>>>

\documentclass[12pt,]{article}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\usepackage[margin=1in]{geometry}
\usepackage{hyperref}
\hypersetup{unicode=true,
            pdftitle={Incorporating dive behaviour into models of marine animal movement},
            pdfborder={0 0 0},
            breaklinks=true}
\urlstyle{same}  % don't use monospace font for urls
\usepackage{longtable,booktabs}
\usepackage{graphicx,grffile}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
\IfFileExists{parskip.sty}{%
\usepackage{parskip}
}{% else
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{5}
% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

@@

  \title{Incorporating dive behaviour into models of marine animal movement}
    \pretitle{\vspace{\droptitle}\centering\huge}
  \posttitle{\par}
    \author{W. J. Grecian\(^1\)\footnote{Corresponding author:
  \href{mailto:james.grecian@gmail.com}{\nolinkurl{james.grecian@gmail.com}}}
, I. D. Jonsen\(^2\)\\
\(^1\)Sea Mammal Research Unit, Scottish Oceans Institute, University of
St Andrews\\
\(^2\)Dept. of Biological Sciences, Macquarie University, Sydney,
Australia}
    \preauthor{\centering\large\emph}
  \postauthor{\par}
      \predate{\centering\large\emph}
  \postdate{\par}
    \date{04 October 2018}

\usepackage{lineno}
\linenumbers
\usepackage{setspace}
\doublespacing

\begin{document}
\maketitle
\begin{abstract}
The Abstract must not exceed 350 words and should list the main results
and conclusions, using simple, factual, numbered statements.\\
1. Models of animal movement often only consider horizontal movement
over 2 dimensions. Incorporating vertical movement in these models
offers the potential to improve our understanding of the drivers of
animal movement.\\
2. Here we describe a state-space model that incorporates a random walk
on both horizontal and vertical movements, and estimates the covariance
between them. The model is flexible to allow both parameters to be
conditioned on covariates, offering insights into the drivers of animal
movement.\\
3. outline the main results\\
4. identify the conclusions and the wider implications.\\
\textbf{keywords:} A list in alphabetical order; not exceeding eight
words or short phrases; The most important key-words should appear in
the title; and the abstract; as well as the key-word list.
\end{abstract}

\begin{verbatim}
## Loading required package: citr
\end{verbatim}

@@

\begin{longtable}[]{@{}lrrrr@{}}
\caption{This is a GLM summary table.}\tabularnewline
\toprule
& Estimate & Std. Error & t value &
Pr(\textgreater{}\textbar{}t\textbar{})\tabularnewline
\midrule
\endfirsthead
\toprule
& Estimate & Std. Error & t value &
Pr(\textgreater{}\textbar{}t\textbar{})\tabularnewline
\midrule
\endhead
(Intercept) & -0.02 & 0.11 & -0.15 & 0.88\tabularnewline
x & 2.00 & 0.12 & 16.76 & 0.00\tabularnewline
\bottomrule
\end{longtable}

@@

The relationship was first described by Halpern, Regan, Possingham, \&
McCarthy (2006). However, there are also opinions that the relationship
is spurious (Keil, Belmaker, Wilson, Unitt, \& Jetz, 2012). We used R
for our calculations (R Core Team, 2016), and we used package.

@@

\section*{REFERENCES}\label{references}
\addcontentsline{toc}{section}{REFERENCES}

\hypertarget{refs}{}
\hypertarget{ref-Halpern_2006}{}
Halpern, B. S., Regan, H. M., Possingham, H. P., \& McCarthy, M. A.
(2006). Accounting for uncertainty in marine reserve design.
\emph{Ecology Letters}, \emph{9}(1), 2--11.
doi:\href{https://doi.org/10.1111/j.1461-0248.2005.00827.x}{10.1111/j.1461-0248.2005.00827.x}

\hypertarget{ref-Keil_2012}{}
Keil, P., Belmaker, J., Wilson, A. M., Unitt, P., \& Jetz, W. (2012).
Downscaling of species distribution models: A hierarchical approach.
\emph{Methods in Ecology and Evolution}, \emph{4}(1), 82--94.
doi:\href{https://doi.org/10.1111/j.2041-210x.2012.00264.x}{10.1111/j.2041-210x.2012.00264.x}

\hypertarget{ref-R_Core_Team_2016}{}
R Core Team. (2016). \emph{R: A language and environment for statistical
computing}. Vienna, Austria: R Foundation for Statistical Computing.
Retrieved from \url{https://www.R-project.org/}
